Distributed computation of linear algebra operations

### 2023-11-08 latex/paper/main.tex
finished slides

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/det_2_10_3.png}
    \centering
    \label{fig:det}
    \caption{Determinant}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/det_2_10_3_detail.png}
    \centering
    \label{fig:det_detail}
    \caption{Detailed plot}
\end{figure}

\subsection{Dot product}
The parallel execution times for the dot product function exhibit a similar trend compared to the determinant function. In this case, the serial execution is generally faster and increases linearly as the matrix size grows. The execution times for both serial and parallel executions are measured in microseconds ($10^{-6}$ seconds) for smaller matrices ($n \le 3$). As the matrix size increases, the performance of the parallel execution degrades, and the execution times become increasingly slower. This is in contrast to the determinant function, where the parallel execution times increased, but the performance was still somewhat decent for smaller matrices. Here, the performance gap between parallel and serial execution widens as the matrix sizes increase, suggesting that the overhead associated with parallelization becomes more pronounced for larger matrices.
\\\\
The standard deviation for serial execution times also rises with matrix size. This indicates an increased variability in execution times for larger matrices in the serial execution. In contrast, the standard deviation for parallel execution times remains relatively stable as matrix size increases, indicating more consistent results across multiple runs.
\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/dot_2_30_5.png}
    \centering
    \label{fig:dot}
    \caption{Dot product}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/dot_2_30_5_detail.png}
    \centering
    \label{fig:dot_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/inv_2_8_3.png}
    \centering
    \label{fig:inv}
    \caption{Inverse}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/inv_2_8_3_detail.png}
    \centering
    \label{fig:inv_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/rank_2_500_5.png}
    \centering
    \label{fig:rank}
    \caption{Rank}
\end{figure}

>>>>

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{../img/det_2_10_3.png}
    \centering
    \label{fig:det}
    \caption{Determinant}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{../img/det_2_10_3_detail.png}
    \centering
    \label{fig:det_detail}
    \caption{Detailed plot}
\end{figure}

\subsection{Dot product}
The parallel execution times for the dot product function exhibit a similar trend compared to the determinant function. In this case, the serial execution is generally faster and increases linearly as the matrix size grows. The execution times for both serial and parallel executions are measured in microseconds ($10^{-6}$ seconds) for smaller matrices ($n \le 3$). As the matrix size increases, the performance of the parallel execution degrades, and the execution times become increasingly slower. This is in contrast to the determinant function, where the parallel execution times increased, but the performance was still somewhat decent for smaller matrices. Here, the performance gap between parallel and serial execution widens as the matrix sizes increase, suggesting that the overhead associated with parallelization becomes more pronounced for larger matrices.
\\\\
The standard deviation for serial execution times also rises with matrix size. This indicates an increased variability in execution times for larger matrices in the serial execution. In contrast, the standard deviation for parallel execution times remains relatively stable as matrix size increases, indicating more consistent results across multiple runs.
\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{../img/dot_2_30_5.png}
    \centering
    \label{fig:dot}
    \caption{Dot product}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{../img/dot_2_30_5_detail.png}
    \centering
    \label{fig:dot_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{../img/inv_2_8_3.png}
    \centering
    \label{fig:inv}
    \caption{Inverse}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{../img/inv_2_8_3_detail.png}
    \centering
    \label{fig:inv_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{../img/rank_2_500_5.png}
    \centering
    \label{fig:rank}
    \caption{Rank}
\end{figure}

### 2023-11-08 latex/presentation/main.tex
finished slides

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{transparent}

@@

return ray.get(futures) 
        \end{lstlisting}
\end{frame}

>>>>

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{transparent}
\usepackage{wasysym}

@@

return ray.get(futures) 
        \end{lstlisting}
\end{frame}
\section{Results of tests}
\begin{frame}[fragile]{Description of tests}
    For our experiments, we considered the following parameters:
\begin{itemize}
    \item \textbf{Determinant calculation:} $n = 2 \dots 10$, each $n$ executed three times.
    \item \textbf{Dot product:} $n = 2 \dots 30$, each $n$ executed five times.
    \item \textbf{Inverse:} $n = 2 \dots 8$, each $n$ executed three times.
    \item \textbf{Rank:} $n = 2 \dots 500$, each $n$ executed five times.
\end{itemize}
\vfill
For each type of operation, the code iterates through different matrix sizes, executing the operation multiple times for each size to capture variations in performance
\end{frame}

\begin{frame}[fragile]{Results of tests (Multiplication)}
    \centering
    \includegraphics[width=\textwidth]{../img/dot_2_30_5.png}
\end{frame}

\begin{frame}[fragile]{Results of tests (Determinant)}
    \centering
    \includegraphics[width=\textwidth]{../img/det_2_10_3.png}
\end{frame}

\begin{frame}[fragile]{Results of tests (Inverse)}
    \centering
    \includegraphics[width=\textwidth]{../img/inv_2_8_3.png}
\end{frame}

\begin{frame}[fragile]{Results of tests (Rank)}
    \centering
    \includegraphics[width=\textwidth]{../img/rank_2_500_5.png}
\end{frame}

\section{Conclusion}
\begin{frame}[fragile]{Conclusion}
    Serial execution always outperforms parallel execution, with both serial execution times and standard deviations sensitive to matrix size. This reveals that the advantages of parallelization are not universally applicable, with the performance gains being countered by overhead in some scenarios.
\end{frame}

\begin{frame}[standout]
    Thanks for reading
    \\
    \Huge\smiley{}
\end{frame}
